---
output: 
  html_document: 
    self_contained: no
    keep_md: yes
    df_print: kable
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=8, fig.height=4, dev = 'png', dpi = 150, 
                      fig.path='assets/figures/', echo=TRUE, warning=FALSE, message=FALSE, 
                      results = 'asis')
```

# R package: caffsim

> Monte Carlo Simulation of Plasma Caffeine Concentrations by Using Population Pharmacokinetic Model

- This package is used for publication of the paper about pharmacokinetics of plasma caffeine.
- Gitbook <http://asancpt.github.io/CaffeineEdison> is created solely dependent on this R package.
- Reproducible research is expected.

## Installation

```{r eval = FALSE}
install.pacakges("devtools")
devtools::install_github("asancpt/caffsim")

# Simply create single dose dataset
caffsim::caffDataset(Weight = 20, Dose = 200, N = 20) 

# Simply create multiple dose dataset
caffsim::caffDatasetMulti(Weight = 20, Dose = 200, N = 20, Tau = 12) 
```

## Single dose

### Create a PK dataset for caffeine single dose

```{r}
library(caffsim)
MyDataset <- caffDataset(Weight = 20, Dose = 200, N = 20)
knitr::kable(head(MyDataset), format = 'markdown')
```

### Create a dataset for concentration-time curve

```{r}
MyConcTime <- caffConcTime(Weight = 20, Dose = 200, N = 20)
knitr::kable(head(MyConcTime), format = 'markdown') 
```

### Create a concentration-time curve

```{r MyPlotMyConcTime}
caffPlot(MyConcTime)
```

### Create plots for publication (according to the amount of caffeine)

- `cowplot` package is required

```{r MyPlotPub, fig.width = 8, fig.height = 12}
#install.packages("cowplot") # if you don't have it
library(cowplot)

MyPlotPub <- lapply(
  c(seq(100, 800, by = 100)), 
  function(x) caffPlotMulti(caffConcTime(20, x, 20)) + 
    theme(legend.position="none") + 
    labs(title = paste0("Single Dose ", x, "mg")))

plot_grid(MyPlotPub[[1]], MyPlotPub[[2]],
          MyPlotPub[[3]], MyPlotPub[[4]],
          MyPlotPub[[5]], MyPlotPub[[6]],
          MyPlotPub[[7]], MyPlotPub[[8]],
          labels=LETTERS[1:8], ncol = 2, nrow = 4)
```

## Multiple dose

### Create a PK dataset for caffeine multiple doses

```{r}
MyDatasetMulti <- caffDatasetMulti(Weight = 20, Dose = 200, N = 20, Tau = 12)
knitr::kable(head(MyDatasetMulti), format = 'markdown') 
```

### Create a dataset for concentration-time curve

```{r}
MyConcTimeMulti <- caffConcTimeMulti(Weight = 20, Dose = 200, N = 20, Tau = 12, Repeat = 10)
knitr::kable(head(MyConcTimeMulti), format = 'markdown')
```

### Create a concentration-time curve

```{r MyPlotMultiMyConcTimeMulti}
caffPlotMulti(MyConcTimeMulti)
```

### Create plots for publication (according to dosing interval)

- `cowplot` package is required

```{r MyPlotMultiPub, fig.width = 8, fig.height = 12}
#install.packages("cowplot") # if you don't have it
library(cowplot)

MyPlotMultiPub <- lapply(
  c(seq(4, 32, by = 4)), 
  function(x) caffPlotMulti(caffConcTimeMulti(20, 250, 20, x, 15)) + 
    theme(legend.position="none") + 
    labs(title = paste0("q", x, "hr" )))

plot_grid(MyPlotMultiPub[[1]], MyPlotMultiPub[[2]],
          MyPlotMultiPub[[3]], MyPlotMultiPub[[4]],
          MyPlotMultiPub[[5]], MyPlotMultiPub[[6]],
          MyPlotMultiPub[[7]], MyPlotMultiPub[[8]],
          labels=LETTERS[1:8], ncol = 2, nrow = 4)
```
