---
output: 
  html_document: 
    self_contained: no
    keep_md: yes
    df_print: kable
  github_document:
    df_print: kable
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(knitr)
knitr::opts_chunk$set(fig.width=8, fig.height=4, dev = 'png', dpi = 150, 
                      fig.path='assets/figures/', echo=TRUE, warning=FALSE, message=FALSE)#, cache = TRUE)
                      #results = 'asis', 
```

# `caffsim` R package: Simulation of Plasma Caffeine Concentrations by Using Population Pharmacokinetic Model

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.842649.svg)](https://doi.org/10.5281/zenodo.842649) 
![CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/caffsim)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/caffsim)](https://cran.r-project.org/package=caffsim)

> Simulate plasma caffeine concentrations using population pharmacokinetic model described in Lee, Kim, Perera, McLachlan and Bae (2015) <doi:10.1007/s00431-015-2581-x> and the package was published <doi:10.12793/tcp.2017.25.3.141>.

- Github: <https://github.com/asancpt/caffsim>
- Package vignettes and references by `pkgdown`: <http://asancpt.github.io/caffsim> 

## Installation

```{r eval = FALSE}
install.pacakges("devtools")
devtools::install_github("asancpt/caffsim")

# Simply create single dose dataset
caffsim::caffPkparam(Weight = 20, Dose = 200, N = 20) 

# Simply create multiple dose dataset
caffsim::caffPkparamMulti(Weight = 20, Dose = 200, N = 20, Tau = 12) 
```

## Single dose

### Create a PK dataset for caffeine single dose

```{r}
library(caffsim)
MyDataset <- caffPkparam(Weight = 20, Dose = 200, N = 20)
head(MyDataset)
```

### Create a dataset for concentration-time curve

```{r}
MyConcTime <- caffConcTime(Weight = 20, Dose = 200, N = 20)
head(MyConcTime)
```

### Create a concentration-time curve

```{r MyPlotMyConcTime}
caffPlot(MyConcTime)
```

### Create plots for publication (according to the amount of caffeine)

- `cowplot` package is required

```{r MyPlotPub, fig.width = 8, fig.height = 12}
#install.packages("cowplot") # if you don't have it
library(cowplot)

MyPlotPub <- lapply(
  c(seq(100, 800, by = 100)), 
  function(x) caffPlotMulti(caffConcTime(20, x, 20)) + 
    theme(legend.position="none") + 
    labs(title = paste0("Single Dose ", x, "mg")))

plot_grid(MyPlotPub[[1]], MyPlotPub[[2]],
          MyPlotPub[[3]], MyPlotPub[[4]],
          MyPlotPub[[5]], MyPlotPub[[6]],
          MyPlotPub[[7]], MyPlotPub[[8]],
          labels=LETTERS[1:8], ncol = 2, nrow = 4)
```

## Multiple dose

### Create a PK dataset for caffeine multiple doses

```{r}
MyDatasetMulti <- caffPkparamMulti(Weight = 20, Dose = 200, N = 20, Tau = 12)
head(MyDatasetMulti)
```

### Create a dataset for concentration-time curve

```{r}
MyConcTimeMulti <- caffConcTimeMulti(Weight = 20, Dose = 200, N = 20, Tau = 12, Repeat = 10)
head(MyConcTimeMulti)
```

### Create a concentration-time curve

```{r MyPlotMultiMyConcTimeMulti}
caffPlotMulti(MyConcTimeMulti)
```

### Create plots for publication (according to dosing interval)

- `cowplot` package is required

```{r MyPlotMultiPub, fig.width = 8, fig.height = 12}
#install.packages("cowplot") # if you don't have it
library(cowplot)

MyPlotMultiPub <- lapply(
  c(seq(4, 32, by = 4)), 
  function(x) caffPlotMulti(caffConcTimeMulti(20, 250, 20, x, 15)) + 
    theme(legend.position="none") + 
    labs(title = paste0("q", x, "hr" )))

plot_grid(MyPlotMultiPub[[1]], MyPlotMultiPub[[2]],
          MyPlotMultiPub[[3]], MyPlotMultiPub[[4]],
          MyPlotMultiPub[[5]], MyPlotMultiPub[[6]],
          MyPlotMultiPub[[7]], MyPlotMultiPub[[8]],
          labels=LETTERS[1:8], ncol = 2, nrow = 4)
```

## Interactive shiny app

```r
caffShiny()
```

